Outputs - civil servants' survey

### 2024-12-20 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

```{r}
exit_mod1 <- lm(INTENT_EXIT_1 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

@@

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

@@

```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

@@

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

@@

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(exit_mod1,exit_mod1_relig,
                  voice_mod1,voice_mod1_relig,
                  work_mod1,work_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))

@@

```{r, fig.width=8,fig.height=6}
p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()

p1

#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
```

>>>>

Alternative Measure for Exit

exit_mod1 <- lm(INTENT_EXIT_1 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

@@

exit_mod3 <- lm(INTENT_EXIT_1 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

#Table A12.3
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T)

@@

exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

@@

exit_mod3 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

#Table A12.4
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T)

@@

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)

#set Other as a base for ministry_by_party
data_for_analysis_senior$ministry_by_party <- relevel(data_for_analysis_senior$ministry_by_party, ref = "Other")
#set Very Senior as a based for ranking
data_for_analysis_senior$ranking <- relevel(data_for_analysis_senior$ranking, ref = "very senior")

@@

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
                            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                          data=data_for_analysis_senior)
politicization_mod1_controls <- politicization_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

sjPlot::tab_model(
                  politicization_mod1,politicization_mod1_controls,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
dv.labels = c("Expected politicization","Expected influence")

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_controls <- influence_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

sjPlot::tab_model(
                  influence_mod1,influence_mod1_controls,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
dv.labels = c("Expected politicization","Expected influence")

@@

Model for exit, voice and work
```{r}

exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
exit_mod3 <- exit_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

sjPlot::tab_model(exit_mod1,
                  exit_mod2,
                  exit_mod3,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
voice_mod3 <- voice_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

sjPlot::tab_model(voice_mod1,
                  voice_mod2,
                  voice_mod3,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)
work_mod3 <- work_mod2 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

sjPlot::tab_model(work_mod1,
                  work_mod2,
                  work_mod3,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)

Models with interactions 
```{r}

#set Other as a base for ministry_by_party
data_for_analysis_senior$ministry_by_party <- relevel(data_for_analysis_senior$ministry_by_party, ref = "Other")
#set very Senior as a based for ranking
data_for_analysis_senior$ranking <- relevel(data_for_analysis_senior$ranking, ref = "very senior")

#exit
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 +   
                  PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
                data=data_for_analysis_senior)
exit_mod1_ministry_by_party_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
exit_mod1_jurist_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )

sjPlot::tab_model(exit_mod1,exit_mod1_ministry_by_party_interaction,exit_mod1_jurist_interaction,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)

#voice

voice_mod1 <- lm(PROJECT_VOICE ~ 
                  BACKSLIDING_2 +   
                  PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
                data=data_for_analysis_senior)
voice_mod1_ministry_by_party_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
voice_mod1_jurist_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )

sjPlot::tab_model(voice_mod1,voice_mod1_ministry_by_party_interaction,voice_mod1_jurist_interaction,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)

#EFFORT

effort_mod1 <- lm(PROJECT_EFFORT ~ 
                   BACKSLIDING_2 +   
                   PAST_POLITICIZATION + PAST_INFLUENCE+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE +education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party,
                 data=data_for_analysis_senior)
effort_mod1_ministry_by_party_interaction <- effort_mod1 %>% update(.~.+ BACKSLIDING_2:ministry_by_party )
effort_mod1_jurist_interaction <- effort_mod1 %>% update(.~.+ BACKSLIDING_2:jurist )

sjPlot::tab_model(effort_mod1,effort_mod1_ministry_by_party_interaction,effort_mod1_jurist_interaction,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)
